Weather Data Integration and Assimilation System\\

### 2020-02-15 method/sec_0_introduction.tex
Complete performance analysis
Grammarly method introduction

This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}.
In \cref{se:high_level_design} a brief discussion on how the weather forecasting is happening and why it need to interact with multiple data formats is presented.
\cref{se:architectural_decisions} that we evolve architectural design while designing and implementing the \acrshort{wdias}.
The \cref{se:microservice} gives better understanding of the microservice architectural concepts follows while implementing the \acrshort{wdias}.
Then the reason behind developing Hierarchical Database and technologies use for that discussed in the \cref{se:db_struct}.
Through out the \cref{se:data_preprocess} discussed about how the \acrshort{wdias} enable for data preprocessing and adding capabilities via concept of Extensions.
Final \cref{se:query} includes details on how to perform timeseries search and Geo based queries.

@@

To get overall idea on the flow of weather prediction, let us look into one of flows using in \acrshort{curw} \cite{CUrWSL2017SL}.
\dbc{Use CUrW-SL}
\gkc{FIXED}

\begin{enumerate}
    \item Extract \acrshort{GRIB} \acrshort{wrf} model data to \acrshort{netCDF}
    \item From \acrshort{netCDF} to \acrshort{csv} of each location data, then feed to HEC-HMS hydro-dynamic model and get the output as \acrshort{csv}
    \item \acrshort{csv} and Rain cell Grid feed into the FLO2D hydro-logic model, and get the water level as ASCII Grid files after completion of simulation
    \item Upload ASCII files to ArcGIS create Raster files, then use for the LOSS Estimation
\end{enumerate}
When looked into the above flow, it clear understanding on multiple data formats using while weather predictions.
Other than that, to correct the model outputs, it required to collect real time data such as;
\begin{itemize}
    \item Automated weather station sending data in higher frequent intervals via HTTP protocol
    \item Automated water level stations send data in higher frequency
\end{itemize}
Other than above there are many data formats using for handling data based on devices and standards which are using. Also, for data modeling, it needs to convert the data into model compatible data format, then after successfully run the model it needs to collect data from the model output data formats.

@@

\paragraph{Integration}-- The system should capable of integrating data from different source such as satellite data, high end and low end weather station etc. And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally. 
\subsubsection{Assimilation}
Then the system should be able to fulfill weather models varying data requirements. Also those models reproduce large set of redundant data, thus system should store the bulk data while optimizing the disk space.
\paragraph{Dissemination}-- Then different users should be able to retrieve data as they required. Also the users should be able to easy to search into the available that in the system base on timeseries metadata or based on Geo queries.

@@

% \subsubsection{Base of WDIAS architecture}
\dbc{What's Base of WDIAS architecture?}
\gkc{Moved to WDIAS microservices section \cref{sebse:wdias_microservices}}

>>>>

This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}.
In \cref{se:high_level_design} a brief discussion on how the weather forecasting is happening and why it needs to interact with multiple data formats is presented.
\cref{se:architectural_decisions} that we evolve architectural design while designing and implementing the \acrshort{wdias}.
\cref{se:microservice} gives a better understanding of the microservice architectural concepts that follow while implementing the \acrshort{wdias}.
Then the reason behind developing \acrshort{wdias} database structure and technologies use for that discussed in \cref{se:db_struct}.
\cref{se:data_preprocess} discussed how the \acrshort{wdias} enables for data preprocessing and adding capabilities via the concept of Extensions.
Final \cref{se:query} includes details on how to perform timeseries search and Geo-based queries.

@@

To get an overall idea of the flow of weather prediction, let us look into one of the flows using in \acrshort{curw} \cite{CUrWSL2017SL}.
\dbc{Use CUrW-SL}
\gkc{FIXED}

\begin{enumerate}
    \item Extract \acrshort{GRIB} \acrshort{wrf} model data to \acrshort{netCDF}
    \item From \acrshort{netCDF} to \acrshort{csv} of each location data, then feed to HEC-HMS hydro-dynamic model and get the output as \acrshort{csv}
    \item \acrshort{csv} and Rain cell Grid feed into the FLO2D hydro-logic model, and get the water level as ASCII Grid files after completion of simulation
    \item Upload ASCII files to ArcGIS create Raster files, then use for the LOSS Estimation
\end{enumerate}
When looked into the above flow, it gives a clear understanding of multiple data formats using while weather predictions.
Other than that, to correct the model outputs, it required to collect real-time data such as;
\begin{itemize}
    \item Automated weather station sending data in higher frequent intervals via HTTP protocol
    \item Automated water level stations send data in higher frequency
\end{itemize}
Other than above many data formats using for handling data based on devices and standards which are using. Also, for data modeling, it needs to convert the data into model compatible data format, then after successfully run the model it needs to collect data from the model output data formats.

@@

\paragraph{Integration}-- The system should capable of integrating data from different sources such as satellite data, high end, and low-end weather station, etc. And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally. 
\subsubsection{Assimilation}
Then the system should be able to fulfill weather models varying data requirements. Also, those models reproduce a large set of redundant data, thus the system should store the bulk data while optimizing the disk space.
\paragraph{Dissemination}-- Then different users should be able to retrieve data as they required. Also, the users should be able to easy to search into the available that in the system base on timeseries metadata or based on Geo queries.

@@

% \subsubsection{Base of WDIAS architecture}
\dbc{What's Base of WDIAS architecture?}
\gkc{Moved to WDIAS database structure section \cref{sebse:wdias_microservices}}

### 2020-02-15 method/sec_1-architectural_decisions.tex
Grammarly method introduction

Initial design of \acrshort{wdias} used the \acrfull{soa}. Moreover, it tried to use an \acrfull{esb} to integrate different modules, as \acrshort{esb} is acting as a common layer for all of modules. By default, \acrshort{esb} also provides publisher/subscribe (pub/sub) capabilities.
\hl{Because} \acrshort{esb} \hl{mediator can be used to integrate the modules which are described in Section} \ref{subse:modules_weather_data_integration_sys}. 
\gkc{FIXED}
The \acrshort{esb} has the processing units called \emph{mediators}. A mediator can take a message, carry out some predefined actions on it, and output the modified message. This mediator capabilities can use to integrate the modules of a weather data system as shown in \cref{fi:wdia_components}. \acrshort{esb} also support different transportation protocols such as HTTP and Web sockets. However, it turned out that \acrshort{esb} is not a suitable for data streaming or bulk data processing. Also, \acrshort{esb} suffer from single point of failure, as all the messages are going though a common bus and slower communication (can’t use for transfer data).

In the second design phase of \acrshort{wdias}, we attempted to use the actor model using AKKA framework \cite{HewittWhyModel} in order to overcome above \acrshort{esb} drawbacks. At the same time, we moved away from the \acrshort{soa} architecture design to the microservice architecture design. Thus we redesign the system architecture with decompose into microservices and used actors to implement each microservice in the system. In that case, an actor or an actor with slave actors were map to each microservice in \acrshort{wdias}. \acrshort{soa} focuses on imperative programming, whereas microservices architecture focuses on a responsive-actor programming style using faster messaging mechanisms.

When compare to \acrshort{soa}, the microservice architecture has several advantages such as the following:
\begin{itemize}
    \item Follow the Single Responsibility principle
    \item Resilient/flexible as failure in one service does not impact other services. If you have monolithic or bulky service errors in one service/module it can impact other modules/functionality.
    \item High scalable as demanding services can be deployed in multiple servers to enhance performance and keep away from other services so that they do not impact other services. Will be difficult to achieve the same with single, large monolithic service.
    \item Easy to enhance as dependencies are less. Is also easier to change and test.
    \item Low impact on other services as each service is independent. % service., this has less chance to impact other services
    \item Easy to understand since they represent a small piece of functionality
    \item Ease of deployment
\end{itemize}

@@

Even with using the AKKA framework, it has some of the disadvantage with implementing each microservice as an actor as described in AKKA documentation \cite{Akka.ioWhenCluster}. One of the attractive feature of microservice architecture is independent nature of the microservices. This allows to choose a different technology for each microservice based on the advantage that could bring in. Also allowed to independently develop and maintain by multiple smaller and more focused teams/communities. But using the actors as microservice, the actors messaging between different services cause to result in a too tight code coupling between the services and difficulties deploying these independent of each other, which is one of the main reasons for using a microservices architecture \cite{Akka.ioWhenCluster}. To overcome these issues, we moved to the concept of container-orchestration based architecture.

@@

Containerization is an alternative to the virtualization that supports via virtual machines or Hypervisors. It involves encapsulating or packaging up software code and all its dependencies so that it can run uniformly and consistently on any infrastructure \cite{IBMContainerizationExplained}. The concept of containerization and process isolation is emerged after the open source Docker Engine \cite{DockerAppContainerization}, an industry standard for package software into standardized units for development, shipment and deployment.

\acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications \cite{LinuxFoundationProduction-GradeKubernetes}. It groups containers that make up an application into logical units for easy management and discovery. While implementing the \acrshort{wdias}, we used \acrshort{k8s} as the container-orchestration system, in order to deploy each microservice as container and manage with providing scalability and availability.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/k8s_architecture_v3.jpg}
    \caption{\acrfull{k8s} architecture.}
    \label{fi:k8s_architecture}
\end{figure}
\cref{fi:k8s_architecture} gives an overall idea on the components of \acrshort{k8s},
\begin{itemize}
    \item Pods -- Cluster of containers that can group other container images in a single unit.
    \item Nodes -- the machines (VMs, physical servers, etc) in a cluster that run your applications and cloud workflows.
    \item kubelet -- An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
    \item kube-proxy -- A network proxy that runs on each node in the cluster, and maintains network rules on nodes.
    \item Kubernetes master -- Responsible for maintaining the desired state for your cluster.
    \item etcd -- Consistent and highly-available key value store used as Kubernetes’ backing store for all cluster data.
\end{itemize}

Users can add much as required Nodes into the \acrshort{k8s} cluster, and \acrshort{k8s} manage and deploy application as pods into cluster nodes.
Each microservice can deploy as a Pod which is a group of containerize applications. And \acrshort{k8s} able to scale as much as user want as described above.
By separating each microservice as a container, and running them as multiple pods inside the \acrshort{k8s} removes the tight coupling of microservices when compared to the actors. This preserves the independent nature of the microservices which allows to high scale the system.

>>>>

The initial design of \acrshort{wdias} used the \acrfull{soa}. Moreover, it tried to use an \acrfull{esb} to integrate different modules, as \acrshort{esb} is acting as a common layer for all of the modules. By default, \acrshort{esb} also provides publisher/subscribe (pub/sub) capabilities.
\hl{Because} \acrshort{esb} \hl{mediators can be used to integrate the modules which are described in Section} \ref{subse:modules_weather_data_integration_sys}. 
\gkc{FIXED}
The \acrshort{esb} has the processing units called \emph{mediators}. A mediator can take a message, carry out some predefined actions on it, and output the modified message. These mediator capabilities can use to integrate the modules of a weather data system as shown in \cref{fi:wdia_components}. \acrshort{esb} also supports different transportation protocols such as HTTP and Web sockets. However, it turned out that \acrshort{esb} is not suitable for data streaming or bulk data processing. Also, \acrshort{esb} suffers from a single point of failure, as all the messages are going through a common bus and slower communication (cant use for transfer data).

In the second design phase of \acrshort{wdias}, we attempted to use the actor model using the AKKA framework \cite{HewittWhyModel} to overcome above \acrshort{esb} drawbacks. At the same time, we moved away from the \acrshort{soa} architecture design to the microservice architecture design. Thus we redesign the system architecture with decomposing into microservices and used actors to implement each microservice in the system. In that case, an actor or an actor with slave actors was a map to each microservice in \acrshort{wdias}. \acrshort{soa} focuses on imperative programming, whereas microservices architecture focuses on a responsive actor programming style using faster messaging mechanisms.

When compare to \acrshort{soa}, the microservice architecture has several advantages such as the following:
\begin{itemize}
    \item Follow the Single Responsibility principle
    \item Resilient/flexible as a failure in one service does not impact other services. If you have monolithic or bulky service errors in one service/module it can impact other modules/functionality.
    \item High scalable as demanding services can be deployed in multiple servers to enhance performance and keep away from other services so that they do not impact other services. It will be difficult to achieve the same with single, large monolithic service.
    \item Easy to enhance as dependencies are less. It is also easier to change and test.
    \item Low impact on other services as each service is independent. % service., this has less chance to impact other services
    \item Easy to understand since they represent a small piece of functionality
    \item Ease of deployment
\end{itemize}

@@

Even with using the AKKA framework, it has some of the disadvantages of implementing each microservice as an actor as described in AKKA documentation \cite{Akka.ioWhenCluster}. One of the attractive features of microservice architecture is the independent nature of the microservices. This allows choosing a different technology for each microservice based on the advantage that could bring in. Also allowed to independently develop and maintain by multiple smaller and more focused teams/communities. But using the actors as microservice, the actors messaging between different services cause to result in a too-tight code coupling between the services and difficulties deploying these independent of each other, which is one of the main reasons for using a microservices architecture \cite{Akka.ioWhenCluster}. To overcome these issues, we moved to the concept of container-orchestration based architecture.

@@

Containerization is an alternative to the virtualization that supports virtual machines or Hypervisors. It involves encapsulating or packaging up software code and all its dependencies so that it can run uniformly and consistently on any infrastructure \cite{IBMContainerizationExplained}. The concept of containerization and process isolation has emerged after the open-source Docker Engine \cite{DockerAppContainerization}, an industry standard for package software into standardized units for development, shipment, and deployment.

\acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications \cite{LinuxFoundationProduction-GradeKubernetes}. It groups containers that make up an application into logical units for easy management and discovery. While implementing the \acrshort{wdias}, we used \acrshort{k8s} as the container-orchestration system, to deploy each microservice as container and manage with providing scalability and availability.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/k8s_architecture_v3.jpg}
    \caption{\acrfull{k8s} architecture.}
    \label{fi:k8s_architecture}
\end{figure}
\cref{fi:k8s_architecture} gives an overall idea on the components of \acrshort{k8s},
\begin{itemize}
    \item Pods -- Cluster of containers that can group other container images in a single unit.
    \item Nodes -- the machines (VMs, physical servers, etc) in a cluster that runs your applications and cloud workflows.
    \item kubelet -- An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
    \item kube-proxy -- A network proxy that runs on each node in the cluster, and maintains network rules on nodes.
    \item Kubernetes master -- Responsible for maintaining the desired state for your cluster.
    \item etcd -- Consistent and highly-available key value store used as Kubernetes’ backing store for all cluster data.
\end{itemize}

Users can add much as required Nodes into the \acrshort{k8s} cluster, and \acrshort{k8s} manage and deploy applications as pods into cluster nodes.
Each microservice can deploy as a Pod which is a group of containerized applications. And \acrshort{k8s} able to scale as much as the user wants as described above.
By separating each microservice as a container, and running them as multiple pods inside the \acrshort{k8s} removes the tight coupling of microservices when compared to the actors. This preserves the independent nature of the microservices which allows to high scale the system.
